Consistent Polyhedral Surrogates via Embedding

### 2019-09-16 notes/top-k.tex
Fixed typo in top-k.tex
Added note in top-k.tex on form of expected loss
Fixing typos

\subsection{Notation and Assumptions}
\subsubsection{Notation}
Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ elements of $u$ and the average of the first $k$ elements of $u$ besides $y$, respectively.
Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
See below in Section~\ref{sec:assumptions} for justification.

@@

Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside the $(\cdot)_+$ operator of $L^{top-k}(u)_y$ is greater than or equal to $0$.
To see this, consider $1 - u_y + \bar u - \frac 1 k = 1 - u_y + \frac k {k-1} \bar u_{-y} + \frac 1 k u_y - \frac 1 k$, and look at the first three elements and the last two.
Since $u_y \geq 1$, the difference between the last two terms $\frac 1 k u_y - \frac 1 k \geq 0$.
Additionally, since $u_y \leq 1 +  \ubar_{-y}$, we can see the sum of these terms is nonnegative.

@@

We can now write the expected loss as follows:
\begin{align*}
\inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 - u_y + \ubar)\\
&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
&= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
\end{align*}

@@

\begin{lemma}\label{lem:linear-pieces}
	For each element $u_i$ of $u$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
	\jessie{Not sure if this is the right statement.}	
\end{lemma}
\begin{proof}
	For all $p \in \simplex$, we know that 
	\begin{equation}
	\inprod{p}{L^{top-k}(u)} = 1 - \bar u + \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
	\end{equation}
	For any $p$, we then have 
	\begin{align*}
	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}\\
	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
	\end{align*}
	which is linear on $u_i$.

	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i$, which is linear in $u_i$.
\end{proof}

@@

By Theorem~\ref{thm:finite-set}, we now have a finite set of optimal reports for $L^{top-k}$.
This yields the finite loss $L|_\R$ embedded by $L^{top-k}$.
This gives the discrete loss $\ell^{top-k} : \R \times\Y \to \reals_+$ by
\begin{align}
\ell^{top-k}(r,y) &= \begin{cases}
0 & u_y = \bar u_{-y} + 1\\
\bar u - \frac 1 k & u_y = 1\\
1 + \bar u & u_y = 0
\end{cases}~.~
\end{align}
\jessie{Not sure if there's more we want to say on this.}

>>>>

\subsection{Notation and Assumptions}
\subsubsection{Notation}
Let $\bar{u} = \frac 1 k \sum_{i = 1}^k u_i$ and similarly, $\bar{u}_{-y} = \frac{1}{k-1} \sum_{i=1, i \neq y}^k u_i$ be the averages of the first $k$ sorted elements of $u$ and the average of the first $k$ sorted elements of $u$ besides $y$, respectively.
Moreover, we say $b = \argmax_i \{u_i : u_i > 1\}$, assuming $u$ is ordered.
See below in Section~\ref{sec:assumptions} for justification.
If each $u_i \leq 1$, then we assign $b = 0$.

@@

Now if $u_y \in (1, \bar u_{-y} + 1]$, then the term inside the $(\cdot)_+$ operator of $L^{top-k}(u)_y$ is greater than or equal to $0$.
To see this, consider $1 - u_y + \bar u - \frac 1 k = 1 - u_y + \frac k {k-1} \bar u_{-y} + \frac 1 k u_y - \frac 1 k$, and look at the first three elements and the last two.
Since $u_y \geq 1$, the difference between the last two terms $\frac 1 k u_y - \frac 1 k \geq 0$.
Additionally, since $u_y \leq 1 +  \ubar_{-y}$, we can see the difference of these terms is nonnegative.

@@

We can now write the expected loss as follows:
\begin{align*}
\inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
%&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
%&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 - u_y + \ubar)\\
%&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
&= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
\end{align*}
%\jessie{I re-wrote the form of the loss at the top of the section, and it seems like this final form of the expected loss is now trivial to get to...?  Right?}

@@

\begin{lemma}\label{lem:linear-pieces}
	For each element $u_i$ of $u$, the expected loss $\inprod{p}{L^{top-k}(u)}$ is linear on $[0,1]$ and $[1, \bar u_{-i} + 1]$ for all $p \in \simplex$.
	\jessie{Not sure if this is the right statement.}	
\end{lemma}
\begin{proof}
	For all $p \in \simplex$, we know that 
	\begin{equation}
	\inprod{p}{L^{top-k}(u)} = 1 - \bar u + \inprod{p}{u + \frac 1 k \min{u,\ones}}~.~
	\end{equation}
	For any $p$, if $u_i \in [0,1]$, we then have 
	\begin{align*}
	\inprod{p}{L^{top-k}(u)} &= 1 + \bar u - \inprod{p}{u + \frac 1 k \min{u,\ones}}\\
	 &= 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i \frac {k+1} k u_i~,~
	\end{align*}
	which is linear on $u_i$.

	Similarly, for $u_i \in [1, \bar u_{-i} + 1]$, we can write $\inprod{p}{L^{top-k}(u)} = 1 + \bar u - \sum_{y \neq i}p_y (u_y + \frac 1 k \min(u_y, 1)) - p_i u_i - p_i/k$, which is linear in $u_i$.
\end{proof}

@@

By Theorem~\ref{thm:finite-set}, we now have a finite set of optimal reports for $L^{top-k}$.
This yields the finite loss $L|_\R$ embedded by $L^{top-k}$.
This gives the discrete loss $\ell^{top-k} : \R \times\Y \to \reals_+$ by
\begin{align}
\ell^{top-k}(r,y) &= \begin{cases}
0 & r_y = \bar r_{-y} + 1\\
\bar r - \frac 1 k & r_y = 1\\
1 + \bar r & r_y = 0
\end{cases}~.~
\end{align}
\jessie{Not sure if there's more we want to say on this.}
